\documentclass{resume} % Use the custom resume.cls style
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{lipsum}
\usepackage{graphicx}
\usepackage{adjustbox}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage[inline]{enumitem}
\usepackage{xcolor}
\usepackage[backend=biber,style=ieee,style=authoryear,maxbibnames=99,defernumbers=true]{biblatex}
\nocite{*}
\date{\today}
\addbibresource{pub.bib}
\makeatletter
\usepackage{hanging}
% This command ignores the optional argument for itemize and enumerate lists
\newcommand{\inlineitem}[1][]{%
\ifnum\enit@type=\tw@
    {\descriptionlabel{#1}}
  \hspace{\labelsep}%
\else
  \ifnum\enit@type=\z@
       \refstepcounter{\@listctr}\fi
    \quad\@itemlabel\hspace{\labelsep}%
\fi}
\makeatother
\parindent=0pt
\usepackage[left=0.3in,top=0.3in,right=0.3in,bottom=0.3in]{geometry} % Document margins
\hyphenpenalty=10000
\DeclareNameAlias{sortname}{given-family}
\DeclareNameAlias{default}{given-family}
\DeclareNameFormat{author}{%
  \nameparts{#1}% split into given/family/etc.
  \ifboolexpr{
    test {\ifdefstring{\namepartfamily}{Datta}}
    and
    test {\ifdefstring{\namepartgiven}{Sohom}}
  }
    {\textbf{\namepartgiven}\space\textbf{\namepartfamily}}
    {\namepartgiven\space\namepartfamily}%
  \ifthenelse{\value{listcount}<\value{liststop}}
    {\addcomma\space}
    {}%
}
\AtEveryBibitem{%
  % Clear the default formatting
  \clearfield{url}
  \clearlist{language}
}

% Redefine inproceedings entries (conference papers)
\DeclareBibliographyDriver{inproceedings}{%
  % --- Title first ---
  \textbf{\printfield[titlecase]{title}}\\
  % --- Authors ---
  \printnames{author}\\
  % --- Venue ---
  \printfield{booktitle}%
  \iffieldundef{year}{}{\space(\printfield{year})}%
  \finentry
}

% Redefine article entries (journals)
\DeclareBibliographyDriver{article}{%
  \printfield[titlecase]{title}%
  \newunit\newblock
  \printnames{author}%
  \newunit\newblock
  \printfield{journaltitle}%
  \iffieldundef{year}{}{\space(\printfield{year})}%
  \finentry
}
\setlength\bibhang{0pt}
\defbibenvironment{bibliography}
  {\begin{list}{$\bullet$}{\leftmargin=1em \itemindent=0em \itemsep -0.6em}}
  {\end{list}}
  {\item}
\newcommand{\tab}[1]{\hspace{.\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Sohom Datta} % Your name
\address{sohomdatta1+web(at)gmail.com}% Your phone number and email
\address {\faWikipediaW \href{https://gerrit.wikimedia.org/r/q/owner:sohomdatta1@gmail.com}{ MediaWiki Gerrit} \\
{\faGithub \href{https://github.com/sohomdatta1}{ GitHub}} \\
{\faLinkedin \href{https://www.linkedin.com/in/sohom-datta-c29ob20k/}{ Linkedin}}}%
\begin{document}
%\vspace{-1em}
\begin{rSection}{Education}
\begin{list}{$\bullet$}{\leftmargin=1em \itemindent=0em}
\itemsep -0.6em
\item {\bf North Carolina State University, Raleigh} \hfill {\em August 2024 -- Ongoing}  \\ PhD in Computer Science (Focus: Web security and privacy)\hfill
\item {\bf Manipal Institute of Technology, Manipal} \hfill {\em July 2019 -- August 2023}  \\ B.Tech in Computer Science and Engineering (Coursework: Compilers, Software testing, Computer security)\hfill
\end{list}
\end{rSection}
\rHeading{Publications}
\printbibliography[heading=none]
\begin{rSection}{Research and Technical Experience}
\begin{rSubsection}{\bf Research Assistant, Wolfpack Security and Privacy Research Lab}{\em January 2024 -- Ongoing}{North Carolina State University}{}
\item Conducted research into privacy-violating JavaScript code across different environments, like mobile browsers and WebViews.
\item Maintained and extended VisibleV8, an open-source browser instrumentation framework across 25+ major Chrome releases.
%\item Built the VisibleV8 Crawler, an open-source tool that enabled internet-scale (around 1M websites) web crawling with VisibleV8.
\item Ported VisibleV8 to Android WebViews, enabling the first dynamic analyses of privacy violations in the Android advertising ecosystem across 1K apps.
\item Designed infrastructure and co-organized HackPackCTF, a competition with 1000+ participants worldwide.
\end{rSubsection}
\begin{rSubsection}{\bf Visiting researcher, Software Security Research Group}{\em September 2023 - December 2023}{Max Planck Institute of Security and Privacy}{}
\item Worked on understanding race-condition bugs in application layer logic in across widely used web servers like Express, and NextJS.
\item Implemented fuzzers to automatically detect and flag security-critical race-condition issues in application logic on web servers.
\end{rSubsection}
\begin{rSubsection}{\bf Student Intern, Wolfpack Privacy and Security Lab}{\em February 2023 - July 2023}{North Carolina State University}{}
%\item Worked on improving VisibleV8, a research tool aimed at making it easier to perform large-scale measurements of web security and abuse patterns on the internet.
\item Implemented large-scale architectural changes to the VisibleV8 crawling pipeline that realized a 20x improvment in crawling and post-processing logs generated by visiting websites.
\item Contributed patches to fix deficiencies in VisibleV8's logging and tracing capabilities, such as it's ability to trace \texttt{eval(...)} and other code execution pathways.
%\item Conducted research into measuring privacy data leakages across cross-party contexts using VisibleV8.
\end{rSubsection}
\begin{rSubsection}{\bf Student Software Developer, Chromium}{\em June 2022 -- November 2022}{Google Summer of Code}{}
\item Worked on aligning Chromium's implementation of the Performance API with the W3C specifications.
\item Discovered and fixed 3 bugs related to incorrect First Contentful Paint and Largest Contentful Paint entries while refactoring the way the PaintTiming API marked contentful images in Chromium.
\item Collaborated with the W3C Web Performance Working Group to rectify an issue in the way LCP timing entries were being reported at the Painting layer.
\item Discovered and patched systemic security issues (cross-site leakages) in the implementation of the ResourceTiming API in the major browser engines, Webkit, Blink and Gecko (Firefox). (\texttt{CVE-2023-1232})
\end{rSubsection}
% \begin{rSubsection}{\bf Research Assistant, Information and Communication Dept.}{\em December 2021 -- June 2022}{Manipal Institute of Technology}{}
% \item Conducted research into inter-process communication mechanisms and their application as a data-exfiltration vector in cross-process Spectre attacks under Professor Nisha P Shetty.
% \item Worked on building a novel obfuscation technique aimed at reducing the efficacy of linkage attacks against ego-centric networks.
% \end{rSubsection}
%\begin{rSection}{Leadership positions}
\begin{rSubsection}{\bf Member, Cryptonite Manipal (cybersecurity student project)}{\em April 2021 -- August 2022}{Manipal Institute of Technology}{}
\item Led a cybersecurity team of 22 engineering students that placed among the top 15 in India in CSAW CTF '21 hosted by NYU (one of the oldest capture the flag competitions for academic teams), secured 2nd place in India in ASIS CTF Finals 2021 and was ranked among the top 12 teams in India on CTFTime in 2021-2022.
\item Created challenges and actively managed the security infrastructure for niteCTF, an international cybersecurity capture the flag event that attracted over 1200+ participants from 43 countries.
\item Conducted workshops on control flow integrity, binary exploitation and format strings exploits detailing the state-of-the-art research in the area, including mitigation techniques such as ASLR, stack cookies, and fuzzy testing.
\item Worked on building a obfuscation technique aimed at reducing the efficacy of linkage attacks against ego-centric social networks.
\end{rSubsection}
\end{rSection}
% \begin{rSubsection}{\bf Web-development Head, Association of Computing Machinery Manipal}{\em August 2021 -- August 2022}{Manipal Institute of Technology}{}
% \item Led and mentored a team of 10 students to develop and maintain infrastructure for a CTF-style inter-college event with 700+ participants.
% \item Conducted workshops and one-on-one sessions to bring the freshers up to speed with modern secure web-development standards demonstrating web security attacks such as cross-site scripting, CSRF, DOM Clobberring etc.
% \end{rSubsection}
%\end{rSection}
\begin{rSection}{Open source experience}
\begin{rSubsection}{ \bf Member, Product and Technology Advisory Council}{ \em October 2024 -- October 2025 }{Wikimedia Foundation}{}
\item Part of a council of 8 volunteers that advised on the technological direction of the Wikimedia movement.
\item Drafted recommendations to assuage community concerns surrounding deployment of artificial intelligence features
\item Led working group to help prioritize work on critical community-facing unmaintained tools that were widely used by the community.
\end{rSubsection}
\begin{rSubsection}{ \bf Lead Maintainer, ProofreadPage}{ \em October 2021 -- Present }{Wikimedia Foundation}{}
\item Maintained the infrastructure for the ProofreadPage extension, which adds proofreading capabilities to MediaWiki and is deployed in over 70 production wikis managed by Wikimedia. (80+ major patches)
\item Improved developer documentation related to the extension, providing guides and detailed walkthroughs regarding its setup and use to help ease the onboarding process for new developers.
\item Introduced Selenium integration tests across the ProofreadPage codebase to better validate critical frontend changes.
\item Took initiative in overhauling the preload and caching mechanism provided by ProofreadPage to decrease load times for editor-facing components.
% \item Built EditInSequence, a community-requested feature that allows users to edit multiple pages via a fast and easy to use interface.
\end{rSubsection}
% \begin{rSubsection}{\bf Google Summer of Code Organization Admin, Wikimedia Foundation}{\em March 2023 -- Sep 2023}{Google Summer of Code}{}
% \item Participated 
% \item 
%
% \end{rSubsection}
\begin{rSubsection}{ \bf Student Software Developer, Wikimedia}{\em March 2020 -- Sep 2020}{Google Summer of Code}{}
\item Developed a software feature that made it easier for volunteers to work with ``pagelist"s, a custom syntax used to store page number information for multi-page files.
\item Developed heuristics that allowed users to create and edit ``pagelist" without interacting with custom XML tag-based syntax.
\item Assisted in developing automated tests to detect accidental/malicious changes in minified JavaScript blobs imported as part of dependencies.
\end{rSubsection}
\end{rSection}
\begin{rSection}{Service}
\begin{list}{}{\leftmargin=1em \itemindent=0em}
\itemsep -0.5em
\item {\bf Artifact reviewer}, IEEE Symposium for Security and Privacy 2026 Artifact Evaluation Committee \hfill {\em (2025 -- Present)}
\item {\bf Member}, Wikimedia Unsupported Tools Working Group \hfill {\em (2025 -- Present)}
\item {\bf Member}, Wikimedia Product and Technology Advisory Council \hfill {\em (2024 -- Present)}
\end{list}
\end{rSection}
\begin{rSection}{Projects}
\begin{list}{$\bullet$}{\leftmargin=1em \itemindent=0em}
\itemsep -0.5em
\item {\bf VisibleV8 crawler} - a open-source tool that enables internet-scale (around 1M websites) web crawling with VisibleV8 which is used extensively internally at the Wolfpack Privacy and Security Lab.
\item {\bf WebViewTracer} - One of the first browser instrumentation frameworks for Android WebViews (an artifact of the Cross-Boundary Mobile Tracking paper which is set to appear in NDSS 2026)
\item {\bf Fuzzing sudo} - Performed a fuzzing campaign on sudo, and found latent use-after-frees, out-of-bound reads and integer overflows. (sudo-project/sudo \texttt{Issue\#198}, \texttt{PR\#196}, \texttt{PR\#218}, \texttt{PR\#227} )
\item {\bf Software sandbox using seccomp-bpf} - Developed a toy process sandbox using the kernel seccomp API that enabled users to selectively allow and deny specific sequences of syscall usages that were considered malicious according to a set of heuristics rules.
%\item {\bf Dis, a stack based language } - Developed a compiler in Typescript for a toy stack-based language that used polish notation to perform arithmetic operations and compiled into x86 assembly.
% \item {\bf Pagelist Widget, a accessibility widget} - Developed a Javascript (ES5) based custom widget that allowed users to interact with a representation of the ''pagelist syntax`` (a syntax based on XML tags) graphically. Additionally, implemented heuristic logic that translated user inputs back into the ''pagelist syntax``.
% \item {\bf Djikstra's pathfinding algorithm in Python} - Developed a distributed system of nodes that dynamically computed the best path inside a maze using the publisher-subscriber model provided by the Robotic Operating System (ROS)
\end{list}
\end{rSection}
\begin{rSection}{Security issues}
\begin{list}{$\bullet$}{\leftmargin=1em \itemindent=0em}
\itemsep -0.6em
\item Found and fixed an authentication bypass, a cross-site scripting and a information disclosure vulnerability in English Wikipedia. (\texttt{CVE-2024-47848}, \texttt{CVE-2024-23174}, \texttt{CVE-2023-45369})
\item Awarded 5000 USD for finding a mechanism to reliably leak a user's browsing history via an experimental ``origin-trial'' web feature in Google Chrome 116.
\item Awarded 7500 USD for finding an XSS sanitization deficiency in the html/template library in Golang. (\texttt{CVE-2023-24538})
\item Awarded 3133.7 USD for discovering authentication bypasses in the dart:core URI parsing module in Dart-lang by the Google Vulnerability Rewards Program in 2022. (\texttt{CVE-2022-3095}, \texttt{GHSA-m9pm-2598-57rj})
\item Awarded 3133.7 USD for discovering a URL validation bypass in Google's Clojure library by the Google Vulnerability Rewards Program in 2021.
\item Found and reported cross-site leakages (XS-leak) issues in Google Chrome and Firefox's implementation of the ResourceTiming API. (\texttt{CVE-2022-1146}, \texttt{CVE-2022-29915})
\item Found and reported a high severity Denial-of-service attack against the popular jpeg-js JavaScript library to snyk.io.
\linebreak(\texttt{CVE-2022-25851}, \texttt{SNYK-JS-JPEGJS-2859218})
\end{list}
\end{rSection}

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages \ & Javascript, C, C++, Python, Golang \\
Domains \ & Browser Internals, Web Security, Dynamic Analysis, Fuzzing \\
Other Software/Frameworks \ & Chromium, Puppeteer, Ghidra, IDA, AFL++, Tensorflow, PostgreSQL, MongoDB \\
\end{tabular}
\end{rSection}
\vspace{1em}
\hrule
\small \small \begin{center}This resume was last updated on \DTMnow. The latest version of this resume is available \href{https://sohomdatta1.github.io/cv/artifacts/cv.pdf}{on Github}.\\
\color{white} The specific commit from which this resume was generated is .\end{center}
\end{document}